How cryptic is cryptic diversity? Machine learning approaches to classifying morphological variation in \textit{Emys marmorata} (Testudinoidea, Emydidae).

### 2013-09-04 documents/turtle_paper.Rnw
added better references on crypsis

% cryptic diversity
%   most species are still deliminated solely based on morphology
Cryptic diversity is the phenomenon that not all taxa can be recognized from morphology and can only be delimited using molecular information \citep{Stuart2006,Pfenninger2007,Funk2012,Clare2011}. Concerningly, most extant taxa, and nearly all extinct taxa, are delimited based solely via morphology. This phenomenon is of great concern when studying variation and diversity dynamics over long periods of time, where apparent morphological stasis may not actually reflect true diversity \citep{Hunt2008,Eldredge1972,Gould1977a,VanBocxlaer2013}. In the case of endangered or conserved taxa, morphometric approaches for classifying and identifying taxa and populations of importance would greatly improve the ability to maintain these high risk groups. Additionally, this could lead to better classification of extinct taxa.

>>>>

% cryptic diversity
%   most species are still deliminated solely based on morphology
Cryptic diversity is the phenomenon that not all taxa can be recognized from morphology and can only be delimited using molecular information \citep{Bickford2007,SchlickSteiner2007,Stuart2006,Pfenninger2007,Funk2012,Clare2011}. Concerningly, most extant taxa, and nearly all extinct taxa, are delimited based solely via morphology. This phenomenon is of great concern when studying variation and diversity dynamics over long periods of time, where apparent morphological stasis may not actually reflect true diversity \citep{Hunt2008,Eldredge1972,Gould1977a,VanBocxlaer2013}. In the case of endangered or conserved taxa, morphometric approaches for classifying and identifying taxa and populations of importance would greatly improve the ability to maintain these high risk groups. Additionally, this could lead to better classification of extinct taxa.
